### 2017-09-30 TF-vldb2018/sec-expt.tex

\etitle{Algorithms}. We implemented the following algorithms, all in C++:
(1) algorithm \optgrouprec for \teamF; (2) incremental algorithm \inc for \dynteamF;
(3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
(a) \mindia is to minimize the team diameter~\cite{Lappas09},
\revise{and is firstly proposed for the team formation problem;}
(b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
(c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
Among algorithms for \teamF, \revise{most of them including  \mindia and \denalk only compute the best team,}
while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
Based on this, we extend \mindia and \denalk to find top-$k$ teams in polynomial time.

@@

Observe the following.
(1) The diameters of teams found by \optgrouprec are comparable to those of \mindia and \minsumdis, which are in particularly designed to minimize the diameters, as shown in Fig.~\ref{fig-exp-semantic-citation-diameter}. This is ensured by the use of balls in \optgrouprec.
(2) The densities of teams found by \optgrouprec, though are smaller than \denalk which is specialized for maximizing team densities, are larger than \mindia and \minsumdis, as shown Fig.~\ref{fig-exp-semantic-citation-density}.
(3) The node satisfiability of teams found by \optgrouprec is much higher than \mindia, \minsumdis and \denalk, \eg 1.0 vs. no larger than 0.2 in all cases as in Fig.~\ref{fig-exp-semantic-citation-capacity}.
(4) The teams found by \optgrouprec come with a higher edge satisfiability , \ie 1.0 in all cases, compared to smaller than 0.6 by \mindia, \minsumdis and \denalk, as shown in Fig.~\ref{fig-exp-semantic-citation-link}.

@@

\revise{These verify that \optgrouprec can effectively preserve structural and capacity constraints for top-$k$ team formation \wrt edge and capacity satisfiability, and pertains a good team collaboration compatibility \wrt density and diameter.}

>>>>

\etitle{Algorithms}. We implemented the following algorithms, all in C++:
(1) algorithm \optgrouprec for \teamF; (2) incremental algorithm \inc for \dynteamF;
(3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
(a) \mindia is to minimize the team diameter~\cite{Lappas09},
\revise{which is firstly proposed for the team formation problem;}
(b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
(c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
\revise{Most of the algorithms for \teamF, including  \mindia and \denalk, only compute the best team,}
while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
Based on this, we extend \mindia and \denalk to find top-$k$ teams in polynomial time.

@@

Observe the following.
(1) The diameters of teams found by \optgrouprec are comparable to those of \mindia and \minsumdis, which are in particularly designed to minimize the diameters, as shown in Fig.~\ref{fig-exp-semantic-citation-diameter}. This is ensured by the use of balls in \optgrouprec.
(2) The densities of teams found by \optgrouprec, though are smaller than \denalk which is specialized for maximizing team densities, are larger than \mindia and \minsumdis, as in Fig.~\ref{fig-exp-semantic-citation-density}.
(3) The node satisfiability of teams found by \optgrouprec is much higher than \mindia, \minsumdis and \denalk, \eg 1.0 vs. no larger than 0.2 in all cases as in Fig.~\ref{fig-exp-semantic-citation-capacity}.
(4) The teams found by \optgrouprec come with a higher edge satisfiability , \eg 1.0 in all cases, compared to smaller than 0.6 by \mindia, \minsumdis and \denalk, as shown in Fig.~\ref{fig-exp-semantic-citation-link}.

@@

\revise{These verify that \optgrouprec can effectively preserve structural and capacity constraints for top-$k$ team formation \wrt edge and node satisfiability, and pertains a good team collaboration compatibility \wrt diameter and density.}
